---
title: "TidyTuesday w33 - Personalities in tv dramas"
date: "22-08-2022
author: "Johnny Lau" ##liamDBailey
output: html_document
---

Focus: 

```{r}

# Load libraries required
library(ggplot2)
library(dplyr)
library(skimr)
library(ggsvg)
library(ggdist)
library(ggtext)
library(scales)


showtext::showtext_auto()
# #FONTS FROM ADOBE FONTS
#sysfonts::font_add(family = "DollyPro", regular = "DollyPro1.otf",
                  # bold = "DollyPro2.otf")
#sysfonts::font_add(family = "AltGothic", regular = "AltGothic7.otf",
                   #bold = "AltGothic4.otf")
#sysfonts::font_add(family = "FormaDJR", regular = "FormaDJR-Regular.otf",
                  # bold = "FormaDJR-Bold.otf")

sysfonts::font_add_google(name = "Anton", "Anton")
sysfonts::font_add_google(name = "Roboto", "Roboto")

knitr::opts_chunk$set(warning=F)


```


# Loading & cleaning data

```{r}
characters  <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-08-16/characters.csv')

psych_stats  <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-08-16/psych_stats.csv')

myers_briggs  <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-08-16/myers_briggs.csv')

```


```{r}
skim(characters)
```


```{r}
characters %>% 
  group_by(name) %>% 
  filter(n() > 1)
```

### Pysch stats
```{r}
skim(psych_stats)
```
- We have 400 different questions across our characters and a rank/rating.
- Does every character have the same number of questions asked about them? Yes

```{r}
psych_stats %>% 
  group_by(char_id) %>% 
  summarise(nQs = length(unique(question))) %>% 
  pull(nQs) %>% 
  unique()
```
###  Myers-Briggs data
- Have 16 unique Meyer-Briggs categories.
- Again, check if they are consistently asked for all characters.

```{r}
myers_briggs %>% 
  group_by(char_id) %>% 
  summarise(nQs = length(unique(myers_briggs))) %>% 
  pull(nQs) %>% 
  unique()
```

## Data wrangling

We will look at average 'kindness' of different universes

```{r}
kind_data <- psych_stats %>% 
  filter(question == "cruel/kind") %>% 
  #Convert to a single metric where avg rating 100 cruel = 0
  mutate(cruel_kind_continuum = case_when(personality == "cruel" ~ abs(avg_rating - 100),
                                          TRUE ~ avg_rating))
```



To check the data, who are the cruelest (and kindest) characters? Seems about right!

```{r}
filter(kind_data, cruel_kind_continuum %in% c(max(cruel_kind_continuum),
                                              min(cruel_kind_continuum)))

```



Get an average rating for every universe.

```{r}
kind_uni <- kind_data %>% 
  group_by(uni_id) %>% 
  summarise(uni_name = first(uni_name),
            mean_kind = mean(cruel_kind_continuum),
            N = n(),
            se = sd(cruel_kind_continuum)/sqrt(n()),
            min_kind = min(cruel_kind_continuum),
            max_kind = max(cruel_kind_continuum)) %>% 
  mutate(across(uni_id:uni_name, .fns = ~forcats::fct_reorder(., .x = mean_kind, .fun = first))) %>% 
  arrange(desc(mean_kind)) %>% 
  mutate(rank_number = 1:n())

kind_uni
```



Arrange factors in both dataset to be arranged by mean kindness

```{r}
plot_data <- kind_data %>% 
  left_join(kind_uni) %>% 
  mutate(across(uni_id:uni_name,
                .fns = ~forcats::fct_reorder(., .x = mean_kind, .fun = first)))

```

## Plot

Plot horizontal bars for each universe plus the avg/SE.

```{r}
#Use hex from RdYlGn palette in Colour Brewer
green_red_palette <- scales:::brewer_pal(type = "div", palette = "RdYlGn")(11)
green_red_palette_dark <- colorspace::darken(green_red_palette, amount = 0.2)

```




```{r}
kind_cruel_plot <- ggplot() +
  geom_vline(xintercept = 50, lty = 2, size = 0.25) +
  stat_gradientinterval(data = plot_data,
                        aes(y = uni_name,
                            x = cruel_kind_continuum,
                            fill = mean_kind),
                        scale = 1,
                        slab_alpha = 0.7,
                        fill_type = "gradient",
                        geom = "slab",
                        slab_type = "pdf", colour = NA,
                        point_interval = "mean_qi") +
  
  
  geom_segment(data = kind_uni,
               aes(x = mean_kind - se,
                   xend = mean_kind + se,
                   y = uni_name,
                   yend = uni_name),
               size = 0.2) +
  geom_point(data = kind_uni,
             aes(y = uni_name, x = mean_kind),
             shape = 21, size = 1.25, stroke = 0.25) +
  geom_text(data = kind_uni,
            aes(y = uni_name, x = 115, label = paste(rank_number, uni_name, sep = ". ")),
            size = 7, hjust = 0, colour = "black",
            family = "Anton") +
  #ADD MANUAL AXIS LINE SO WE CAN LIMIT THE EXTENT
  geom_segment(aes(x = 100, xend = 0, y = 101, yend = 101),
               size = 0.25, lineend = "round") +
  #ADD MANUAL TITLE ABOVE AXIS
  geom_richtext(aes(x = c(75, 25),
                    y = 100,
                    label = c(paste0("<span style='color:",
                                     green_red_palette[11],
                                     ";'>Kind</span>"),
                              paste0("<span style='color:",
                                     green_red_palette[1],
                                     ";'>Cruel</span>"))),
                label.colour = NA, fontface = "bold", size = 20,
                fill = NA, hjust = 0.5, vjust = -0.6,
                family = "DollyPro") +
  #Titles and labels
  labs(title = "WHO HAS THE KINDEST* CHARACTERS?",
       subtitle = paste0("Police dramas, like Criminal Minds and NCIS, have the KINDEST characters on average<br>In comparison, comedy TV shows have some of the  CRUELEST characters,<br> like Always Sunny, Veep, and Archer."),
       caption = "Plot: @ldbailey255 | Data: openpsychometrics.org<br>* A characters score is aggregated from millions of users who rate fictional characters on a continuum from cruel to kind.") +
  scale_fill_gradientn(colours = green_red_palette_dark) +
  scale_x_continuous(position = "top",
                     breaks = seq(100, 0, -25),
                     minor_breaks = seq(100, 0, -12.25),
                     labels = c(100, 50, 0, 50, 100)) +
  coord_fixed(clip = "off", ratio = 1.8,
              xlim = c(120, -20),
              expand = FALSE) +
  theme_classic() +
  theme(axis.ticks.y = element_blank(),
        axis.ticks.x = element_line(size = 0.25, lineend = "round"),
        axis.text.y = element_blank(),
        axis.title = element_blank(),
        axis.line = element_blank(),
        axis.text.x = element_markdown(colour = "black", size = 35,
                                       family = "AltGothic"),
        legend.position = "none",
        plot.margin = margin(r = 10, l = 20, t = 5, b = 5),
        plot.title = element_markdown(size = 80,
                                      margin = margin(l = 10, b = 7, t = 10),
                                      family = "Roboto"),
        plot.subtitle = element_markdown(margin = margin(l = 10, b = 20),
                                         size = 40, lineheight = 0.2,
                                         family = "Roboto"),
        plot.caption = element_markdown(size = 30, family = "Roboto", lineheight = 0.1),
        plot.background = element_rect(fill = "#fafafa", colour = NA),
        panel.background = element_rect(fill = "#fafafa", colour = NA))

ggsave(here::here("w33_personality/Week33.png"), plot=kind_cruel_plot, height = 6, width = 4, dpi = 600)

```
